---
title: "Homework"
output: html_document
date: "2022-10-20"
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For the homework, you will be given a differentially expressed gene file in csv format.<br />
You need to read data into a dataframe, filter and add some columns, and create a volcano plot.


```{r library, message=FALSE, warning=FALSE, include=TRUE,error=FALSE}
#You will need following packages to finish the homework
library(dplyr)
library(ggplot2)
```

### 1. Read table
Load "differentially_expressed_genes.csv" into a dataframe
```{r read table, include=TRUE,warning=FALSE,error=TRUE}
#read your table and load it onto deg variable below
deg<-

```

### 2. Manipulate your data frame
You will need 3 columns (avg_log2FC, p_val_adj, GENE) only for further downstream analysis.<br> Use select function to get those 3 columns.<br> After, create a new column with a column name log10_pval_adj and -log10(pval_adj) as value. (note: log10 is default R function to calculate log10 of given value)
Lastly, you need to add another column name "upordown" to tell whether your gene is up or down regulated. You can check the directionality of genes by looking at avg_log2FC (if avg_log2FC > 0 up or avg_log2FC < 0 down).
```{r Select and Mutate dataframe, include=TRUE,warning=FALSE,error=TRUE}
#Add your code here
deg.filtered <- 
```

### 3. Generate a volcano plot
Now you are all ready to generate volcano plot. Use ggplot() and geom_point() to generate the plot
Which column is used for x axis, y axis, and color?

```{r Volcano plot, include=TRUE,warning=FALSE,error=TRUE}
#Add your code here
#plot<-ggplot(deg.filtered,aes())+geom_point()

plot<-ggplot(deg.filtered,aes())+geom_point()

plot
```

#### Important!! Please write down the following information
Approximately, how long did it take to finish the homework? <Write your hours or minutes here><br />
Name: <Write your name here><br />
Student number: <Write your student number here><br />
Email: <Write your email here><br />


#### Knit your rmarkdown file into a html file and submit it to 
<smha118@ucla.edu> with header "Intro to R - Homework"
 


